The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-01-18 SC-challenge.tex
added emails

Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University;
A.\ M.\ Smith,
GitHub, Inc.;
D.\ S.\ Katz,
Computation Institute, University of Chicago \& Argonne National Laboratory.
\end{bottomstuff}

>>>>

Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University;
A.\ M.\ Smith,
GitHub, Inc.;
D.\ S.\ Katz,
Computation Institute, University of Chicago \& Argonne National Laboratory;
emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
\end{bottomstuff}
